Bird beak's elaboration and exploration

### 2021-11-04 Analysis/03.1-results.Rmd
Update 03.1-results.Rmd

```{r, echo = FALSE}
## Plot the results
wrap.plot <- function(results, col, main) {
    ## How many sub plots?
    n <- length(results)
    ## Edit names for cleaning
    # for(i in 1:n) {
    #     names(results[[i]]$disparity) <- gsub(":phylogeny", "", names(results[[i]]$disparity))
    # }

    ## Which will be the centre plot?
    centre <- 1
    ## Plot everything
    op <- par(mfrow = c(n, 1), mar = c(7, 4, 4, 2) + 0.1)
    for(i in 1:n) {
        plot(results[[i]], col = col, main = ifelse(i == centre, main, ""), las = 2, xlab = "")
    }
    par(op)
}
wrap.plot(results$super_results_between,
          col = rainbow(n.subsets(superorder_shapespace)-1),
          main = "Superorders differences")
```
Figure: these results show the projections ("position"), rejection ("distance") and angles ("degree") of the posteriors of each group's major axes onto the corresponding global phylogenetic major axes. For each panel, the highest the score the more the clade is elaborating, exploring, exploring perpendicular to the main axes for the position, distance and degree respectively.

```{r, fig.height = 20, fig.width = 10, echo = FALSE}
wrap.plot(results$order_results_between,
          col = rainbow(n.subsets(order_shapespace)-1),
          main = "Superorders differences")
```

@@

```{r, fig.height = 20, fig.width = 10, echo = FALSE, eval = FALSE}
## Plot the results
wrap.plot(results$super_results_phylo,
          col = rainbow(n.subsets(superorder_shapespace)-1),
          main = "Projections per superorder\non the global phylogeny axes")
```
Figure: the projection of each species per group onto the posterior distribution of global major phylogenetic axis.

@@

## Plot the results
wrap.plot(results$order_results_phylo,
          col = rainbow(n.subsets(order_shapespace)-1),
          main = "Projections per order\non the global phylogeny axes")
```

@@

## Plot the results
wrap.plot(results$super_results_within,
          col = rainbow(n.subsets(superorder_shapespace)-1),
          main = "Projections per superorder\nonto each superorder")
```
Figure: the projection of each species per group onto the posterior distribution of each clade's major phylogenetic axis (the grey distributions corresponds to the projections of all the species, irregardless of their group, onto the global phylogenetic major axes).

@@

## Plot the results
wrap.plot(results$order_results_within,
          col = rainbow(n.subsets(order_shapespace)-1),
          main = "Projections per order\nonto each order")
```

>>>>

```{r, echo = FALSE}
## Plot the results
wrap.plot <- function(results, col, main, names) {

    ## Adding one plot
    one.plot <- function(one_result, xlab, col, zero = TRUE, main, ...) {
        values <- lapply(get.disparity(one_result, concatenate = FALSE), c)
        boxplot(values, horizontal = TRUE, yaxt = "n", col = col, xlab = xlab, main, ...)
        if(zero) {
            abline(v = 0, col = "black", lty = 3, lwd = 1)
        }
    }

    ## How many sub plots?
    n <- length(results)

    ## Recycle labels?
    if(missing(names)) {
        names_list <-names(results)
    } else {
        names_list <- names
    }

    ## Which will be the centre plot?
    centre <- ceiling(n/2)
    ## Plot everything
    op <- par(mfrow = c(1, n+1))
    ## Plot the first panel
    par(bty = "n", mar = c(5, 5, 4, 0) + 0.1)
    empty <- matrix(0, ncol = length(results[[1]]$disparity))
    colnames(empty) <- names(results[[1]]$disparity)
    boxplot(empty, horizontal = TRUE, las = 2, col = "white", ylim = c(0,0), xaxt = "n", border = "white")
    for(i in 1:n) {
        par(mar = c(5, 0, 4, 0) + 0.1, bty = "o")
        one.plot(results[[i]], col = col, main = ifelse(i == centre, main, ""), xlab = names_list, zero = (names(results)[[i]] == "position"))
    }
    par(op)
}
wrap.plot(results$super_results_between,
          col = rainbow(n.subsets(superorder_shapespace)-1),
          main = "Superorders differences",
          names = c("elaboration", "innovation", "angle"))
```
Figure: these results show the projections ("position"), rejection ("distance") and angles ("degree") of the posteriors of each group's major axes onto the corresponding global phylogenetic major axes. For each panel, the highest the score the more the clade is elaborating, exploring, exploring perpendicular to the main axes for the position, distance and degree respectively.

```{r, fig.height = 20, fig.width = 10, echo = FALSE}
wrap.plot(results$order_results_between,
          col = rainbow(n.subsets(order_shapespace)-1),
          main = "Superorders differences",
          names = c("elaboration", "innovation", "angle"))
```

@@

```{r, fig.height = 20, fig.width = 10, echo = FALSE, eval = FALSE}
## Plot the results
wrap.plot(results$super_results_phylo,
          col = rainbow(n.subsets(superorder_shapespace)-1),
          main = "Projections per superorder\non the global phylogeny axes",
          names = c("elaboration", "innovation", "angle"))
```
Figure: the projection of each species per group onto the posterior distribution of global major phylogenetic axis.

@@

## Plot the results
wrap.plot(results$order_results_phylo,
          col = rainbow(n.subsets(order_shapespace)-1),
          main = "Projections per order\non the global phylogeny axes",
          names = c("elaboration", "innovation", "angle"))
```

@@

## Plot the results
wrap.plot(results$super_results_within,
          col = rainbow(n.subsets(superorder_shapespace)-1),
          main = "Projections per superorder\nonto each superorder",
          names = c("elaboration", "innovation", "angle"))
```
Figure: the projection of each species per group onto the posterior distribution of each clade's major phylogenetic axis (the grey distributions corresponds to the projections of all the species, irregardless of their group, onto the global phylogenetic major axes).

@@

## Plot the results
wrap.plot(results$order_results_within,
          col = rainbow(n.subsets(order_shapespace)-1),
          main = "Projections per order\nonto each order",
          names = c("elaboration", "innovation", "angle"))
```
